---
title: "Project_Proposal"
author: "Collin O'Connor"
date: "10/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem / Question:

The deer tick or blacklegged tick (<i>Ixodes scapularis</i>) is the most medically relevant species of hard tick that in New York State (NYS). <i>I. scapularis</i> populations in NYS may carry a plethora of pathogens, including but not limited to:

* <i>Borrelia burgdorferi</i> - the causitive agent of Lyme disease
* <i>Anaplasma phagocytophilum</i> - the causitive agent of human granulocytic anaplasmosis
* <i>Babesia microti</i> - the causitive agent of babesiosis in humans
* <i>Borrelia miyamotoi</i> - causative of a relapsing tick fever 

The prevalence of the above pathogens varies both spatially and temporally in NYS, which results in varying risk for NYS citizens. 










```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
